SPARQL on the Open, Decentralised Web

### 2016-11-21 dissertation/conclusions.tex
Proofreading corrections

Problem~\ref{prob:queryeq} is has an interesting possible solution in
the application of hashing algorithms that have a reasonable chance of
returning the same digest if two queries are equivalent. As noted in
Section~\ref{sec:relcache}, \cite{kaseicache} can be used for this. It
is also interesting to discuss the approach \cite{papailiou2015graph}
took to canonical labelling in HTTP context:

>>>>

Problem~\ref{prob:queryeq} has an interesting possible solution in
the application of hashing algorithms that have a reasonable chance of
returning the same digest if two queries are equivalent. As noted in
Section~\ref{sec:relcache}, \cite{kaseicache} can be used for this. It
is also interesting to discuss the approach \cite{papailiou2015graph}
took to canonical labelling in HTTP context:
